Colonies - Compute Continuums across Platforms

### 2023-04-17 paper_2023/paper.tex
wip

To address these challenges, the paper presents an open-source framework called Colonies\footnote{https://github.com/colonyos/colonies}, which facilitates execution of computational workloads across a diverse range of platforms. Colonies enables development of a \emph{distributed runtime environment}, called a \emph{Colony}, which can effortlessly integrate with any third-party application or other workflow systems.

Based on a stateless microservice architecture, complex workflows can be broken down into composable functions. These composable functions can be implemented in any programming language and be executed by distributed executors deployed across platforms, anywhere on the Internet such as IoT, cloud, edge, and supercomputers. A zero-trust security protocol enables a collection of distributed executors to operate as a unified entity, establishing seamless compute continuums across platforms.

@@

The long-term vision of the Colonies framework is to enable uninterrupted access to computing resources, allowing data to flow from one service to another establishing a seamlessly integrated computing ecosystem. To realize this vision, the paper presents Colonies, a \emph{distributed runtime environment} designed to easily integrate with third-party systems. The remainder of the paper describes the Colonies framework and how it can be used to create robust and scalable compute continuums.

@@

Figure 1 depicts an overview of the components part of the Colonies framework. The \emph{Colonies servers} form the backbone of the framework, functioning as a centralized control system for task submission and assignment. The Colonies server acts as a job broker for executors, almost like an employment agency for people. All execution information and history are stored in a database maintained by the Colonies servers. Upon submission, a process is stored in the database, serving as a queueing system. When a process is assigned to an executor its execution status is changed from \emph{waiting} to \emph{running}. Consequently, it is possible to submit a process that should run in the future even if no executors can run the process at the moment. In this way, Colonies supports both batch and real-time processing.

@@

\section{Discussion}
This paper has presented an open-source framework called Colonies, which is designed to streamline execution of computational workloads across platforms. Colonies enable the creation of a \emph{distributed runtime environment}, called a \emph{Colony}, which serves as an intermediary layer to indirectly control and integrate with other computer systems. Instead of directly connecting different systems together, Colonies allows services or users to publish instructions and then assign these instructions to other services. By chaining instructions together, it becomes possible to execute workloads that can operate seamlessly across different platforms.

@@

While microservices is a powerful design pattern, Colonies goes beyond the conventional microservice model and offers a distributed microservice architecture that allows microservices to reside anywhere on the Internet. Also, by acting as an intermediary layer, Colonies provides a unified interface to facilitate interaction between these microservices, making it possible to create workflows that span multiple platforms. For instance, Colonies could be used to expose an entire HPC system as a microservice and then connected it to other microservices running in the cloud or IoT devices.

In summary, the primary objective of Colonies is to offer uninterrupted access to computing resources, allowing data to flow from one service to another. Achieving seamless compute continuum requires development of simple, secure, scalable, and robust solutions. Colonies serves as an initial step towards realizing the vision of a seamlessly integrated computing ecosystem.

>>>>

To address these challenges, the paper presents an open-source framework called Colonies\footnote{https://github.com/colonyos/colonies}, which facilitates execution of computational workloads across a diverse range of platforms. Colonies provides a \emph{distributed runtime environment}, called a \emph{Colony}, which can effortlessly integrate with any third-party application or other workflow systems.

Based on a stateless microservice architecture, complex workflows can be broken down into composable functions. These composable functions can be implemented in any programming language and be executed by distributed executors deployed across platforms, anywhere on the Internet such as IoT, cloud, edge, or a supercomputer. A zero-trust security protocol enables a collection of distributed executors to operate as a unified entity, establishing seamless compute continuums across platforms.

@@

The long-term vision of the Colonies framework is to enable uninterrupted access to computing resources, allowing data to flow from one service to another establishing a seamlessly integrated computing ecosystem. To realize this vision, the paper presents \emph{Colonies}, a \emph{distributed runtime environment}. The remainder of the paper describes the Colonies framework and how it can be used to create robust and scalable compute continuums.

@@

Figure 1 depicts an overview of the components part of the Colonies framework. The \emph{Colonies servers} form the backbone of the framework, functioning as a centralized control system for task submission and assignment. The Colonies server serves as a job broker for executors, almost like an employment agency for people. All execution information and history are stored in a database maintained by the Colonies servers. Upon submission, a process is stored in the database, serving as a queueing system. When a process is assigned to an executor its execution status is changed from \emph{waiting} to \emph{running}. Consequently, it is possible to submit a process that should run in the future even if no executors can run the process at the moment. In this way, Colonies supports both batch and real-time processing.

@@

\section{Discussion}
This paper has presented an open-source framework called Colonies, which is designed to streamline execution of computational workloads across platforms. Colonies provides a \emph{distributed runtime environment}, called a \emph{Colony}, which serves as an intermediary layer to indirectly control and integrate with other computer systems. Instead of directly connecting different systems together, Colonies allows services or users to publish instructions and then assign these instructions to other services. By chaining instructions together, it becomes possible to execute workloads that can operate seamlessly across different platforms.

@@

While microservices is a powerful design pattern, Colonies goes beyond the conventional microservice model and offers a distributed microservice architecture allowing microservices to reside anywhere on the Internet. Also, by acting as an intermediary layer, Colonies provides a unified interface to facilitate interaction between these microservices, ultimately making it possible to create workflows that span multiple platforms. The paper has also presented into several use cases related to edge computing, cloud computing and high-performance computing, highlighting the benefits that such a framework could provide, in particular how to create loosely-coupled systems that offers both flexibility, robustness, and scalability.

To sum up, the long-term vision of the Colonies framework is to offer uninterrupted access to computing resources, allowing data to flow from one service to another. Achieving seamless compute continuum requires development of simple, secure, scalable, and robust solutions. Colonies serves as an initial step towards realizing this vision of a seamlessly integrated computing ecosystem.
